Motor Learning Without Moving

### 2019-07-14 ManuscriptMaterials.Rmd
minor revisions to address review

---
title: "Motor Learning Without Moving"
subtitle: "Figures and Statistics"
author:
- Ahmed A. Mostafa
- Bernard Marius 't Hart
- Denise Henriques
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
---

>>>>

---
title: "Motor Learning Without Moving"
subtitle: "Figures and Statistics"
author:
- Ahmed A. Mostafa
- Bernard Marius 't Hart
- Denise Henriques
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
---
